LAGOS lake depth

### 2020-05-04 figures/01_contrasts.Rmd
look at shoreline dev by shape class

>>>>

```{r gg_shorelinedev_shape_class, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# compare shoreline dev for each shapeclass
gg_shorelinedev_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%  
  contrast_plot(grp = "shape_class", varb = "lake_shorelinedevfactor_nounits", 
                label = "Shoreline Dev.", plot_type = "pointrange")
```
